Mahotas: Open source software for scriptable computer vision

### 2013-03-20 paper.tex
REF Reference imglib2

Mahotas is a computer vision library for the Python Programming Language
(versions 2.5 and up, including version 3 and up). It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information and performing basic manipulations and
computations. In particular, unlike libraries written in the C~Language or in
Java~\citep{Marcel:2010:TMP:1873951.1874254}, Mahotas does not need to define a
new image data structure, but uses the numpy array structure. Many basic
manipulation functionality that would otherwise be part of a computer vision
library are handled by numpy. For example, computing averages and other simple
statistics, handling multi-channel images, converting between types (integer
and floating point images are supported by mahotas) can all be performed with
numpy builtin functionality. For the user, this has the additional advantage
that they do not need to learn yet another set of functions.

>>>>

Mahotas is a computer vision library for the Python Programming Language
(versions 2.5 and up, including version 3 and up). It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information and performing basic manipulations and
computations. In particular, unlike libraries written in the C~Language or in
Java~\citep{Pietzsch15112012,Marcel:2010:TMP:1873951.1874254}, Mahotas does not need to define a
new image data structure, but uses the numpy array structure. Many basic
manipulation functionality that would otherwise be part of a computer vision
library are handled by numpy. For example, computing averages and other simple
statistics, handling multi-channel images, converting between types (integer
and floating point images are supported by mahotas) can all be performed with
numpy builtin functionality. For the user, this has the additional advantage
that they do not need to learn yet another set of functions.
